### 2023-10-28 doc/Thesis/chapter/061-results-emma.tex
finish todos

%GENERATIONS
In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
The green points at generation number 0 indicate particles which were not included to be propagated. 
%Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
Violet lines connect individual particles in time. 
The blue line connects averages of particles of each generation (including initial non-propagated particles) and 
yellow lines connect averages of each generation of only those particles which were propagated. 
%
Both $\gamma$ and $\rho$ were to be minimized and show a clear trend towards low values with increasing generation, 
indicating that the optimization worked even though 
the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
and the chosen samples (i.e. chosen input variables) where not exactly as expected. 
Neither expected were the measurements for these samples.
The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
Measurements were expected to show clear correlation of optimizands $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
The only statistically relevant correlation was observed for $T_{cal}$ with the optimizands.
%\td{why}
%
In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature~$T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{
		(a)~calculated conductance measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
		\td{
		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
	change colors }
	\td{increase font in gnuplot, change y-axis of (c)}
	}

>>>>

%GENERATIONS
In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
The green points at generation number 0 indicate particles which were not included to be propagated. 
%Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
Violet lines connect individual particles in time. 
The blue line connects averages of particles of each generation (including initial non-propagated particles) and 
yellow lines connect averages of each generation of only those particles which were propagated. 
%
Both $\gamma$ and $\rho$ were to be minimized and show a clear trend towards low values with increasing generation, 
indicating that the optimization worked even though 
the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
and the chosen samples (i.e. chosen input variables) where not exactly as expected. 
Neither expected were the measurements for these samples.
The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
Measurements were expected to show clear correlation of \textit{optimizands} $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
The only statistically relevant correlation was observed for $T_{cal}$ with the \textit{optimizands}.
%\td{why}
%
In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature~$T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{
		(a)~calculated conductance measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
	change colors }

### 2023-10-28 doc/Thesis/chapter/063-discussion.tex
finish todos

Moreover, it is important to define the objective of the project as clear and unambiguous as possible. 
Again, try to reformulate the objective in multiple ways and choose the most fitting. 
Answer which question should be answered, and establish hypotheses with corresponding null hypotheses. 
A general experimental design procedure was stated by Cherkassky and Mulier in  ``Learning from Data''\cite{cherkassky1998learning}:
\begin{enumerate}
    \item {State the problem}
    \item {Formulate the hypothesis}
    \item {Design the experiment/data generation process}
    \item {Collect the data and perform preprocessing}
    \item {Estimate the model}
    \item {Interpret the model/draw the conclusion}
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Narrowing, pre-optimization and constraint phase}
\label{sec:phase2}
The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} %(page 25)
After having decided on a base recipe, it is important to define limits and decrease the number of independent variables. 
The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of data points. 
By excluding input variables from the model, 
the complexity of the model can be drastically reduced. 
This leads to more information which can be extracted from the remaining data, 
be it in more detail of the dependence or higher confidence interval. 
A good measure to compare with literature and other methods is the \gls{epv}. 
The \gls{epv} in this work is round 5,
which is low in comparison with literature consulted
\cite{
ahmed2017preparation,
fernandes2010multi,
kaczmarowski2015genetic,
mahdavi2017hardness,
soltanali2014neural,
panwar2014design,
schubert2008design,
shanaghi2013experimental}.
Reducing variables is of course no easy task.
How does one decide which variables to keep and which to incorporate into the model and which to discard? 
There is an intuitive (expert) way and a mathematical way.
An expert would decide which variables to discard by his expert knowledge about the domain. 
Mathematical ways include principal component analysis and step-wise regression.
%
Additionally, having wide limits can be an advantage when the data is noisy and the dependence is not too complicated, because by moving samples to the boundaries of the design space, the effect of the noise is reduced\cite{giunta2003overview}. 
This suggest variable reduction favorable over limit narrowing.
%"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
%
There are two opposing principles which should be kept in mind when reducing variables, though:
By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect\cite{gunst2009fractional}.
On the other hand a model can be used to tell if a variable exerts an influence\cite{haertler2014statistisch}. 
%
%One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
Another reason to avoid too many variables in a model is that they introduce more parameters to fit and overfitting happens in the regime where to many parameters are fitted with not enough data.
%todo{Overfitting happens in the regime where to many parameters are fitted with not enough data. }

Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimization 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization, modelling and data generation phase}
\label{sec:phase3}
During the optimization the main problems were too many in- and output variables, reproducibility and regularization. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimization the input data were not regularized, %es wurde auf regularization verzichtet, 
because the regularization would be different for different generations.
Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
These were the reasons for not including regularization during \gls{emma} optimization. 
On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardization the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\iffalse
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
\end{itemize}
\fi

@@

\td{when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

>>>>

Moreover, it is important to define the objective of the project as clear and unambiguous as possible. 
Again, try to reformulate the objective in multiple ways and choose the most fitting. 
Answer which question should be answered, and establish hypotheses with corresponding null hypotheses. 
A general experimental design procedure was stated by Cherkassky and Mulier in  ``Learning from Data''\cite{cherkassky1998learning}:
    \item {State the problem}
    \item {Formulate the hypothesis}
    \item {Design the experiment/data generation process}
    \item {Collect the data and perform preprocessing}
    \item {Estimate the model}
    \item {Interpret the model/draw the conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Narrowing, pre-optimization and constraint phase}
\label{sec:phase2}
The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} %(page 25)
After having decided on a base recipe, it is important to define limits and decrease the number of independent variables. 
The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of data points. 
By excluding input variables from the model, 
the complexity of the model can be drastically reduced. 
This leads to more information which can be extracted from the same amount of data, 
be it in more detail of the dependence or higher confidence interval. 
A good measure to compare data density with literature and other methods is the element per variable ratio.
The \gls{epv} in this work is round 5,
which is low in comparison with literature consulted
\cite{
ahmed2017preparation,
fernandes2010multi,
kaczmarowski2015genetic,
mahdavi2017hardness,
soltanali2014neural,
panwar2014design,
schubert2008design,
shanaghi2013experimental}.
Reducing variables is of course no easy task.
How does one decide which variables to keep and which to incorporate into the model and which to discard? 
There is an intuitive (expert) way and a mathematical way.
An expert would decide which variables to discard by his expert knowledge about the domain. 
Mathematical ways include principal component analysis and step-wise regression.
%
Additionally, having wide limits can be an advantage when the data is noisy and the dependence is not too complicated, because by moving samples to the boundaries of the design space, the effect of the noise is reduced\cite{giunta2003overview}. 
This suggest variable reduction favorable over limit narrowing.
%"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
%
There are two opposing principles which should be kept in mind when reducing variables, though:
By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect\cite{gunst2009fractional}.
On the other hand a model can be used to tell if a variable exerts an influence\cite{haertler2014statistisch}. 
%
%One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
Another reason to avoid too many variables in a model is that they introduce more parameters to fit and overfitting happens in the regime where too many parameters are fitted with not enough data.
%todo{Overfitting happens in the regime where to many parameters are fitted with not enough data. }
%
Another step which is well placed in this phase is the estimate the measuring error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimization 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization, modelling and data generation phase}
\label{sec:phase3}
During the optimization the main problems were too many in- and output variables, reproducibility and regularization. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimization the input data were not regularized (scaled), %es wurde auf regularization verzichtet, 
although this could have increased the efficiency of the model.
%because the regularization would be different for different generations.
%Regularizing with the mean and standard deviation would be either inconsistent across generations or \td{overvalue the distribution of the initial generation.}
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
%These were the reasons for not including regularization during \gls{emma} optimization. 
%On the other hand 
The input data could have been regularized to only take values $[-1;1]$ by defining the regularized variable as 
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardization the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 

@@

%\td{0when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

### 2023-10-28 doc/Thesis/chapter/07-outlook.tex
finish todos

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing its stability. 
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A strong correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

>>>>

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in an insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing the stability of the solution. 
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
